The development of abstract concepts in children's early lexical networks

### 2019-02-28 CMCL/ms.Rmd
ms

First, we constructed the end-state network based on all nouns learned by the last age of acqusition. We used a subset of CDI nouns for which cross-linguistic translations are present, allowing us to explore cross-linguistic variability. We used data from the ten following languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish. The size of this subset varied from `r max_n` in Russian (representing `r max_per`% of total nouns in this language) to `r min_n` in Turkish (representing `r min_per`% of total nouns). Second, in order to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.

@@

```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages. Colors indicates real and hypothetical word sampling mechanisms. Errors bars represent 95\\% confidence intervals."}

measurements <- readRDS("data/measurements.rds")
meas_rand <- readRDS("data/cluster_randomization_measurements.rds")

@@

#all_rand <- meas_rand %>%
#  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
#         #randomization != "to_nearest_aoa",
#         n_clusters != '5') %>%
#  as.data.frame()

@@

#all_sum_rand <- all_rand %>%
#  group_by(measure, cluster_randomization, age) %>%
#  multi_boot_standard(col = "value", na.rm = TRUE)
  #summarise(myMean = mean(value, na.rm = TRUE))

all_sum$measure <- mapvalues(all_sum$measure, from = c("pair_precision_to_last", "pair_recall_to_last"), to = c("Precision", "Recall"))
all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Exploration","Exploitation"))

all_sum_corr <- all_sum %>%
  as.data.frame() %>%
  select(-ci_lower, -ci_upper) %>%
  spread(randomization, mean) %>%
  group_by(measure) %>%
  dplyr::summarise(sim = round(cor(Real, Exploration)^2, 2),
            seq = round(cor(Real, Exploitation)^2, 2))

@@

all_sum$randomization <- factor(all_sum$randomization, levels = c("Real", "Exploration","Exploitation"))

@@

$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
Where $tp(\mathcal{C}_t)$ are the true positives, defined as the word pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$. $fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$. Finally, $fn(\mathcal{C}_t)$ are the false positives defiened as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.

We made this comparison using different degrees of clustering granularity. More precisely, we fixed the same number of clusters for both $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters. We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.

@@

>>>>

First, we constructed the end-state network based on all nouns learned by the last age of acquisition. We used a subset of CDI nouns for which cross-linguistic translations are present, allowing us to explore cross-linguistic variability. We used data from the ten following languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish. The size of this subset varied from `r max_n` in Russian (representing `r max_per`% of total nouns in this language) to `r min_n` in Turkish (representing `r min_per`% of total nouns). Second, in order to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.

@@

```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, averaged across languages and numbers of clusters. Colors indicates real and hypothetical word sampling mechanisms. Errors bars represent 95\\% confidence intervals."}

measurements <- readRDS("data/measurements.rds")
#meas_rand <- readRDS("data/cluster_randomization_measurements.rds")

@@

##all_rand <- meas_rand %>%
#  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
#         #randomization != "to_nearest_aoa",
 #                 n_clusters != '5') %>%
 #as.data.frame()

@@

#all_sum_rand <- all_rand %>%
#  group_by(measure, language, cluster_randomization, age) %>%
# multi_boot_standard(col = "value", na.rm = TRUE)
  #summarise(myMean = mean(value, na.rm = TRUE))

all_sum$measure <- mapvalues(all_sum$measure, from = c("pair_precision_to_last", "pair_recall_to_last"), to = c("Precision", "Recall"))
all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Simultaneous","Sequential"))

all_sum_corr <- all_sum %>%
  as.data.frame() %>%
  select(-ci_lower, -ci_upper) %>%
  spread(randomization, mean) %>%
  group_by(measure) %>%
  dplyr::summarise(sim = round(cor(Real, Simultaneous)^2, 2),
            seq = round(cor(Real, Sequential)^2, 2))

@@

all_sum$randomization <- factor(all_sum$randomization, levels = c("Real", "Simultaneous","Sequential"))

@@

$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
Where $tp(\mathcal{C}_t)$ are the true positives, defined as the word pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$. $fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$. Finally, $fn(\mathcal{C}_t)$ are the false positives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.

We made this comparison using different degrees of clustering granularity. More precisely, we fixed the same number of clusters for *both* $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters. We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.

@@

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}
